Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-10 preliminaries.tex
Fix typos

\Ethan{Look up ``interactive protocols for BQP"}
\begin{definition}
	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
	\Ethan{TODO: errors are functions of input length}
	\begin{itemize}
		\item If $x\in L$
			$\Pr\left[(P, V)(x)=(1^n, x)\right]$
		\item TODO SOUNDNESS
	\end{itemize}
\end{definition}

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x)$. \Ethan{Same problem as last definition...} Then $d=rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
\end{definition}

>>>>

\Ethan{Look up ``interactive protocols for BQP"}
\begin{definition}
	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item If $x\in L$, then $\Pr\left[(P, V)(x)=\Rej\right]<c(\abs{x})$.
		\item If $x\notin L$, then for all cheating prover $P^*$, $\Pr\left[(P^*, V)(x)=\Acc\right]<s(\abs{x})$.
	\end{itemize}
\end{definition}

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
\end{definition}
